Modelling Prehistoric Iconographic Compositions. The \proglang{R} package \pkg{decorr}

### 2020-12-04 article_rvTH16.tex
rerun 16

Symbolic practices is a characteristic trait of human societies. Even discussed, such practices seems to start between 233,000 to 800,00 BC \citep{dErrico00}, covering more than 97\% of total human societies time span. Symbolism cover a large range of practices, from ochre deposit in a tomb, to menhir alignements, passing through wall fresco. This latter, what might be called "iconographical practices", probably shows the most complex and interesting testimonies of past societies symbolism. For decades, its study was linked to history of religion because commonly seen as closely linked to cultual practices and believes. Since the \textit{New Archaeology} developpement during the 60's \citep{Clarke14}, symbolic expressions start to be studied with the same formal methods (statistics, seriations, distribution maps, etc.) as any another aspect of social organisation: settlement patterns, tools \emph{chaine op\'eratoire}, susbsitence strategies, etc. \citep{Renfrew91}. But unlike many aspects of the material culture where technological requirements and technical efficiency determine the choice of the raw material and the shape of the object -- a flint blade for cutting, a pottery for containing, a house for living --, the function of an iconographic composition cannot be drawn directly from itself. Whether these last decades study of ancient iconography had  undergone significative improvements at the site scale -- with GIS/database statistics, paleoenvironmental restitutions, etc. -- and at the sign scale with the development of archaeological sciences -- radiocarbon dating, use-wear analysis, elemental analysis, etc. --, these improvement do not necessarly help to understand the semantic content of the iconography.

Semantics or semiotics can be defined as a system of conventional features -- called signs -- organised also in conventional manners. Until our days, formal methods to study ancient iconography semantics have been mostlty been grounded  -- explicitly or not -- on the prime principle of Saussurian linguistic: the '\emph{linearity of the signifier}' \citep{Saussure89}.  
Writing is one of the most rational semiographical system with a clear distinction between signified and signifier and the development of the signified on a linear axis. Even if we do not understand the meaning of the signs, writing can easily be modelled with Graph theory and recurent patterns can be identified. For example, the 3-letters word "\code{art}" can be modelled with three vertices (\code{a}, \code{r}, \code{t}) and two edges (one between \code{a} and \code{r}, the other between \code{r} and \code{t}). In \proglang{R}, these features, concatenated in this order with a \code{paste0()}, is \code{art}, and not \code{rat}.
\smallbreak
\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/a_r_t-1}

@@

The inventory of decorations is stored in the \code{imgs} dataframe. The field \code{imgs$idf} is the short name of the decoration, useful during statistical analysis. The primary key of each decoration is the concatenate of \code{imgs$site} and \code{imgs$decor}. These keys will allow joints with the other dataframes (\code{nodes} and \code{edges})\\
%
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:29 2020
\begin{table}[H]
\centering
\begin{tabular}{|p{0.5cm}|p{2.5cm}|p{2.5cm}|p{8.5cm}|}
  \hline
idf & site & decor & img \\ 
  \hline
  1 & Cerro Muriano & Cerro Muriano 1 & Cerro\_Muriano.Cerro\_Muriano\_1.jpg \\ 
    2 & Torrejon Rubio & Torrejon Rubio 1 & Torrejon\_Rubio.Torrejon\_Rubio\_1.jpg \\ 
    3 & Brozas & Brozas & Brozas.Brozas.jpg \\ 
    4 & Zarza de Montanchez & Zarza De Montanchez & Zarza\_de\_Montanchez.Zarza\_De\_Montanchez.jpg \\ 
    5 & Ibahernando & Ibahernando & Ibahernando.Ibahernando.jpg \\ 
   \hline
\end{tabular}
\caption{The studied corpus, the \code{imgs.tsv} dataframe} 
\label{Test_table}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Nodes (from \\code{nodes.csv} dataframe)}"
R> print(xtable::xtable(head(nodes),
+                       caption = caption),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:31 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrr}
  \hline
 & site & decor & id & type & x & y \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 & personnage & 349.81 & -298.32 \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   2 & casque & 349.81 & -243.99 \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 & lance & 238.46 & -298.32 \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   4 & bouclier & 446.02 & -381.17 \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   5 & peigne & 283.00 & -358.01 \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   7 & sexe\_masculin & 342.69 & -427.49 \\ 
   \hline
\end{tabular}
\caption{Nodes (from \code{nodes.csv} dataframe)}} 
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Edges (from \\code{edges.csv} dataframe)}"
R> print(xtable::xtable(head(edges),
+                 caption=caption,
+                 label="edgesdf"),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:31 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrl}
  \hline
 & site & decor & a & b & type \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 &   4 & = \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   1 &   5 & = \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 &   5 & = \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   1 &   2 & + \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   1 &   7 & + \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   3 &   1 & = \\ 
   \hline
\end{tabular}
\caption{Edges (from \code{edges.csv} dataframe)}} 
\label{edgesdf}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> lgrph <- list_dec(imgs,nodes,edges,var="type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in list\_dec(imgs, nodes, edges, var = "{}type"{}): unused argument (var = "{}type"{})}}\begin{verbatim}
R> plot(lgrph[[1]],
+       vertex.color = "orange",
+       vertex.frame.color="orange",
+       vertex.label.color = "black",
+       vertex.size = 8,
+       vertex.label.cex = 0.6,
+       edge.color = "orange",
+       vertex.label.family="Helvetica"
+  )
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot(lgrph[[1]], vertex.color = "{}orange"{}, vertex.frame.color = "{}orange"{}, : object 'lgrph' not found}}\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> # library(decorr)
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".shp",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(nds.df[6,],
+                       # caption="Sixth node (GU 6) of the Torrejon Rubio 1 decoration",
+                       label="nd",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:35 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrr}
  \hline
 & site & decor & id & type & x & y \\ 
  \hline
13 & Torrejon Rubio & Torrejon Rubio 1 &   6 & epee & 366.70 & -563.14 \\ 
   \hline
\end{tabular}
\label{nd}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(eds.df[1,],
+                       # caption="First edge of the Torrejon Rubio 1 decoration, the proximity between the sword (GU 6) and the fibula (GU 5)",
+                       label="eds.df",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:35 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrlrrrr}
  \hline
 & site & decor & a & b & type & xa & ya & xb & yb \\ 
  \hline
9 & Torrejon Rubio & Torrejon Rubio 1 &   6 &   5 & = & 366.70 & -563.14 & 490.12 & -513.24 \\ 
   \hline
\end{tabular}
\label{eds.df}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> # library("decorr")
R> par(mar=c(0,0,0,0))
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> img.graph <- plot_dec_grph(nodes = nds.df,
+                             edges = eds.df,
+                             site = sit,
+                             decor = dec,
+                             doss = system.file("extdata", package = "decorr"),
+                             lbl.txt = "type",
+                             lbl.size=2)
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_dec\_grph(nodes = nds.df, edges = eds.df, site = sit, decor = dec, : unused argument (lbl.txt = "{}type"{})}}\begin{verbatim}
R> plot(image_trim(img.graph))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in assert\_image(image): object 'img.graph' not found}}\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> # par(mar=c(0,0,0,0))
R> g.compar <- list_compar(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in utils::combn(1:length(lgrph), 2): object 'lgrph' not found}}\begin{verbatim}
R> eds_compar <- plot_compar(g.compar, c(1,4),
+                            focus = "edges",
+                            doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_compar(g.compar, c(1, 4), focus = "{}edges"{}, doss = system.file("{}extdata"{}, : object 'g.compar' not found}}\begin{verbatim}
R> plot(magick::image_trim(magick::image_read(eds_compar)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in magick::image\_read(eds\_compar): path must be URL, filename or raw vector}}\end{kframe}

@@

\begin{itemize}
\setlength\itemsep{.1em}
  \item \code{same_nds()} and \code{same_eds()} functions allow to repectively count matching nodes and matching edges between decoration pairwises
\end{itemize}

\code{same_nds()} and \code{same_eds()} allow to repectively count matching nodes and matching edges between decoration pairwises. The result is a square matrix between all pairwise comparisons with the number of common nodes or edges in the cells. For example, we can compute the matrix of common edges.

\begin{kframe}
\begin{verbatim}
R> df.same_edges <- same_neds(lgrph, "type", "edges")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in same\_neds(lgrph, "{}type"{}, "{}edges"{}): could not find function "{}same\_neds"{}}}\begin{verbatim}
R> caption <- "Number of same edges between all decoration pairwise comparisons"
R> print(xtable::xtable(df.same_edges,
+                       caption = caption,
+                       label = "Test_table_2",
+                       size = 8,
+                       digits = c(0)),
+        table.placement="H",
+        include.rownames = TRUE)
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable::xtable(df.same\_edges, caption = caption, label = "{}Test\_table\_2"{}, : object 'df.same\_edges' not found}}\end{kframe}

@@

\begin{table}[H]
\begin{minipage}{.45\textwidth}
\centering
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in same\_neds(lgrph, "{}type"{}, "{}edges"{}): could not find function "{}same\_neds"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in same\_neds(lgrph, "{}type"{}, "{}nodes"{}): could not find function "{}same\_neds"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(df.same\_nodes, digits = c(0)): object 'df.same\_nodes' not found}}\end{kframe}
\captionof{table}{Common nodes table}
\end{minipage}
\begin{minipage}{.45\textwidth}
\centering
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(df.same\_edges, digits = c(0)): object 'df.same\_edges' not found}}\end{kframe}
\captionof{table}{Common edges table}
\end{minipage}
\end{table}

@@

\begin{figure}[H]
\begin{kframe}
\begin{verbatim}
R> library("matlib")
R> par(mfrow=c(1,2))
R> dist.nodes  <- dist(inv(as.matrix(df.same_nodes)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in as.matrix(df.same\_nodes): object 'df.same\_nodes' not found}}\begin{verbatim}
R> dist.edges  <- dist(inv(as.matrix(df.same_edges)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in as.matrix(df.same\_edges): object 'df.same\_edges' not found}}\begin{verbatim}
R> plot(hclust(dist.nodes), hang = -1, main = "common nodes")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hclust(dist.nodes): object 'dist.nodes' not found}}\begin{verbatim}
R> plot(hclust(dist.edges), hang = -1, main = "common edges")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hclust(dist.edges): object 'dist.edges' not found}}\end{kframe}
\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> par(mar=c(0,0,0,0))
R> par(mfrow=c(2,1))
R> g.compar <- list_compar(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in utils::combn(1:length(lgrph), 2): object 'lgrph' not found}}\begin{verbatim}
R> nds_compar.3.4 <- plot_nds_compar(g.compar, c(3,4),
+                                    doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_nds\_compar(g.compar, c(3, 4), doss = system.file("{}extdata"{}, : could not find function "{}plot\_nds\_compar"{}}}\begin{verbatim}
R> plot(image_read(nds_compar.3.4))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(nds\_compar.3.4): object 'nds\_compar.3.4' not found}}\begin{verbatim}
R> # g.compar <- list_eds_compar(lgrph,"type")
R> eds_compar.3.4 <- plot_eds_compar(g.compar, c(3,4),
+                                doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_eds\_compar(g.compar, c(3, 4), doss = system.file("{}extdata"{}, : could not find function "{}plot\_eds\_compar"{}}}\begin{verbatim}
R> plot(image_read(eds_compar.3.4))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(eds\_compar.3.4): object 'eds\_compar.3.4' not found}}\end{kframe}

>>>>

Symbolic practices is a characteristic trait of human societies. Even discussed, such practices seems to start between 233,000 to 800,00 BC \citep{dErrico00}, covering more than 97\% of total human societies time span. Symbolism cover a large range of practices, from ochre deposit in a tomb, to menhir alignements, passing through wall fresco. This latter, what might be called "iconographical practices", probably shows the most complex and interesting testimonies of past societies symbolism. For decades, its study was linked to history of religion because commonly seen as closely linked to cultual practices and believes. Since the \textit{New Archaeology} developpement during the 60's \citep{Clarke14}, symbolic expressions start to be studied with the same formal methods (statistics, seriations, distribution maps, etc.) as any another aspect of social organisation: settlement patterns, tools \emph{chaine op\'eratoire}, susbsitence strategies, etc. \citep{Renfrew91}. But unlike many aspects of the material culture where technological requirements and technical efficiency determine the choice of the raw material and the shape of the object -- a flint blade for cutting, a pottery for containing, a house for living --, the function of an iconographic composition cannot be drawn directly from itself. Whether these last decades study of ancient iconography had  undergone significative improvements at the site scale -- with GIS/database statistics, paleoenvironmental restitutions, etc. -- and at the sign scale with the development of archaeological sciences -- radiocarbon dating, use-wear analysis, elemental analysis, etc. --, these improvement do not necessarly help to understand the semantic content of the iconography.\\
Semantics or semiotics can be defined as a system of conventional features -- called signs -- organised also in conventional manners. Until our days, formal methods to study ancient iconography semantics have been mostlty been grounded  -- explicitly or not -- on the prime principle of Saussurian linguistic: the '\emph{linearity of the signifier}' \citep{Saussure89}.  
Writing is one of the most rational semiographical system with a clear distinction between signified and signifier and the development of the signified on a linear axis. Even if we do not understand the meaning of the signs, writing can easily be modelled with Graph theory and recurent patterns can be identified. For example, the 3-letters word "\code{art}" can be modelled with three vertices (\code{a}, \code{r}, \code{t}) and two edges (one between \code{a} and \code{r}, the other between \code{r} and \code{t}). In \proglang{R}, these features, concatenated in this order with a \code{paste0()}, is \code{art}, and not \code{rat}.
\smallbreak
\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth,height=0.5\textheight]{figure/a_r_t-1}

@@

The inventory of decorations is stored in the \code{imgs} dataframe. The field \code{imgs$idf} is the short name of the decoration, useful during statistical analysis. The primary key of each decoration is the concatenate of \code{imgs$site} and \code{imgs$decor}. These keys will allow joints with the other dataframes (\code{nodes} and \code{edges})\\
%
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:04 2020
\begin{table}[H]
\centering
\begin{tabular}{|p{0.5cm}|p{2.5cm}|p{2.5cm}|p{8.5cm}|}
  \hline
idf & site & decor & img \\ 
  \hline
  1 & Cerro Muriano & Cerro Muriano 1 & Cerro\_Muriano.Cerro\_Muriano\_1.jpg \\ 
    2 & Torrejon Rubio & Torrejon Rubio 1 & Torrejon\_Rubio.Torrejon\_Rubio\_1.jpg \\ 
    3 & Brozas & Brozas & Brozas.Brozas.jpg \\ 
    4 & Zarza de Montanchez & Zarza De Montanchez & Zarza\_de\_Montanchez.Zarza\_De\_Montanchez.jpg \\ 
    5 & Ibahernando & Ibahernando & Ibahernando.Ibahernando.jpg \\ 
   \hline
\end{tabular}
\caption{The studied corpus, the \code{imgs.tsv} dataframe} 
\label{Test_table}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Nodes (from \\code{nodes.csv} dataframe)}"
R> print(xtable::xtable(head(nodes),
+                       caption = caption),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:05 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrr}
  \hline
 & site & decor & id & type & x & y \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 & personnage & 349.81 & -298.32 \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   2 & casque & 349.81 & -243.99 \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 & lance & 238.46 & -298.32 \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   4 & bouclier & 446.02 & -381.17 \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   5 & peigne & 283.00 & -358.01 \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   7 & sexe\_masculin & 342.69 & -427.49 \\ 
   \hline
\end{tabular}
\caption{Nodes (from \code{nodes.csv} dataframe)}} 
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Edges (from \\code{edges.csv} dataframe)}"
R> print(xtable::xtable(head(edges),
+                       caption=caption,
+                       label="edgesdf"),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:05 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrl}
  \hline
 & site & decor & a & b & type \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 &   4 & = \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   1 &   5 & = \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 &   5 & = \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   1 &   2 & + \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   1 &   7 & + \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   3 &   1 & = \\ 
   \hline
\end{tabular}
\caption{Edges (from \code{edges.csv} dataframe)}} 
\label{edgesdf}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> lgrph <- list_dec(imgs,nodes,edges)
R> plot(lgrph[[1]],
+       vertex.color = "orange",
+       vertex.frame.color="orange",
+       vertex.label.color = "black",
+       vertex.size = 8,
+       vertex.label.cex = 0.6,
+       edge.color = "orange",
+       vertex.label.family="Helvetica"
+  )
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/igraph-1}

\caption{\label{fig:figs}R interface. Plot of the first graph of the list}\label{fig:igraph}
\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> # library(decorr)
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".shp",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(nds.df[6,],
+                       # caption="Sixth node (GU 6) of the Torrejon Rubio 1 decoration",
+                       label="nd",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:06 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrr}
  \hline
 & site & decor & id & type & x & y \\ 
  \hline
13 & Torrejon Rubio & Torrejon Rubio 1 &   6 & epee & 366.70 & -563.14 \\ 
   \hline
\end{tabular}
\label{nd}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(eds.df[1,],
+                       # caption="First edge of the Torrejon Rubio 1 decoration, the proximity between the sword (GU 6) and the fibula (GU 5)",
+                       label="eds.df",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:06 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrlrrrr}
  \hline
 & site & decor & a & b & type & xa & ya & xb & yb \\ 
  \hline
9 & Torrejon Rubio & Torrejon Rubio 1 &   6 &   5 & = & 366.70 & -563.14 & 490.12 & -513.24 \\ 
   \hline
\end{tabular}
\label{eds.df}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> # library("decorr")
R> par(mar=c(0,0,0,0))
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> img.graph <- plot_dec_grph(nodes = nds.df,
+                             edges = eds.df,
+                             site = sit,
+                             decor = dec,
+                             doss = system.file("extdata", package = "decorr"),
+                             nds.lbl = "type",
+                             lbl.size=2)
R> plot(image_trim(img.graph))
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/tr_st-1}

\caption{\label{fig:figs}Torrejon Rubio 1 decoration}\label{fig:tr_st}
\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> # par(mar=c(0,0,0,0))
R> g.compar <- list_compar(lgrph,"type")
R> eds_compar <- plot_compar(g.compar, c(1,4),
+                            focus = "edges",
+                            doss = system.file("extdata", package = "decorr"))
R> plot(magick::image_trim(magick::image_read(eds_compar)))
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-6-1}

\caption{\label{fig:figs}comparisons between 1 (Cerro Muriano 1) and 4 (Zarza de Montsanchez) decorations}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\begin{itemize}
\setlength\itemsep{.1em}
\item \code{same_elements()} function allows to count matching nodes and matching edges between decoration pairwises
\end{itemize}

\code{same_elements()} allows to count matching nodes and matching edges between decoration pairwises. The result is a square matrix between all pairwise comparisons with the number of common nodes or edges in the cells. For example, we can compute the matrix of common edges.

\begin{kframe}
\begin{verbatim}
R> df.same_edges <- same_elements(lgrph, "type", "edges")
R> caption <- "Number of same edges between all decoration pairwise comparisons"
R> print(xtable::xtable(df.same_edges,
+                       caption = caption,
+                       label = "Test_table_2",
+                       size = 8,
+                       digits = c(0)),
+        table.placement="H",
+        include.rownames = TRUE)
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:10 2020
\begin{table}[H]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & 1 & 2 & 3 & 4 & 5 \\ 
  \hline
1 & 8 & 0 & 1 & 2 & 0 \\ 
  2 & 0 & 15 & 3 & 7 & 1 \\ 
  3 & 1 & 3 & 10 & 1 & 2 \\ 
  4 & 2 & 7 & 1 & 14 & 1 \\ 
  5 & 0 & 1 & 2 & 1 & 4 \\ 
   \hline
\end{tabular}
\caption{Number of same edges between all decoration pairwise comparisons} 
\label{Test_table_2}
\end{table}

@@

\begin{table}[H]
\begin{minipage}{.45\textwidth}
\centering
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:10 2020
\begin{table}[H]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & 1 & 2 & 3 & 4 & 5 \\ 
  \hline
1 & 7 & 2 & 3 & 4 & 2 \\ 
  2 & 2 & 12 & 5 & 9 & 3 \\ 
  3 & 3 & 5 & 6 & 4 & 3 \\ 
  4 & 4 & 9 & 4 & 12 & 3 \\ 
  5 & 2 & 3 & 3 & 3 & 4 \\ 
   \hline
\end{tabular}
\end{table}

\captionof{table}{Common nodes table}
\end{minipage}
\begin{minipage}{.45\textwidth}
\centering
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 11:03:10 2020
\begin{table}[H]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & 1 & 2 & 3 & 4 & 5 \\ 
  \hline
1 & 8 & 0 & 1 & 2 & 0 \\ 
  2 & 0 & 15 & 3 & 7 & 1 \\ 
  3 & 1 & 3 & 10 & 1 & 2 \\ 
  4 & 2 & 7 & 1 & 14 & 1 \\ 
  5 & 0 & 1 & 2 & 1 & 4 \\ 
   \hline
\end{tabular}
\end{table}

\captionof{table}{Common edges table}
\end{minipage}
\end{table}

@@

\begin{figure}[H]
\begin{kframe}
\begin{verbatim}
R> library("matlib")
R> par(mfrow=c(1,2))
R> dist.nodes  <- dist(inv(as.matrix(df.same_nodes)))
R> dist.edges  <- dist(inv(as.matrix(df.same_edges)))
R> plot(hclust(dist.nodes), hang = -1, main = "common nodes")
R> plot(hclust(dist.edges), hang = -1, main = "common edges")
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/unnamed-chunk-10-1}

\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> par(mar=c(0,0,0,0))
R> par(mfrow=c(2,1))
R> g.compar <- list_compar(lgrph,"type")
R> nds_compar.3.4 <- plot_compar(g.compar, c(3,4),
+                                focus = "nodes",
+                                doss = system.file("extdata", package = "decorr"))
R> plot(magick::image_read(nds_compar.3.4))
R> # g.compar <- list_eds_compar(lgrph,"type")
R> eds_compar.3.4 <- plot_compar(g.compar, c(3,4),
+                                focus = "edges",
+                                doss = system.file("extdata", package = "decorr"))
R> plot(magick::image_read(eds_compar.3.4))
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}

\caption{\label{fig:figs}Decoration comparisons between 3 and 4}\label{fig:unnamed-chunk-11}
\end{figure}
